Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
section 7

The @ndcps@ itself is implemented with delimited controls. 
The function takes two arguments: a set of elements with type @T@ and an initial 
accumulated value of type @Set[S]@. 
Function @ndcps@ iteratively returns a value of type @T@ with annotated by
@@cps[Set[T]]@ that denotes the final returned value of @ndcps@ is type @Set[T]@.
The @f@ introduced by the @shift@ operator is the delimited continuation at the 
call-site of @ndcps@.

@@

We add an annotation @@cps[Ans]@ on the return type of function @aeval@.
Now for every non-deterministic choices in the abstract interpreter

@@

>>>>

The @ndcps@ itself is implemented with delimited controls. 
The function takes two arguments: a set of elements with type @T@ and an initial 
accumulated value of type @Set[S]@. 
Function @ndcps@ iteratively returns a value of type @T@ with annotated by
\texttt{\@ cps[Set[T]]} that denotes the final returned value of @ndcps@ is type @Set[T]@.
The @f@ introduced by the @shift@ operator is the delimited continuation at the 
call-site of @ndcps@.

@@

We add an annotation \texttt{ cps[Ans]} on the return type of function @aeval@.
Now for every non-deterministic choices in the abstract interpreter, we can simply use
@ndcps@ on them and write the program sequentially as a concrete interpreter.
The cache is still accumulated to the next call to @ndcps@ or @aeval@ given the 
fact that the abstract interpreter should always use the latest cache.

@@

The function @analyze@ is also changed by adding a @reset@ around the function call to @aeval@.
